---
title: "Global soil hydraulic properties (GSHP) database"
author: "Surya Gupta, Andreas Papritz, Peter Lehmann, Tom Hengl, Sara Bonetti, Dani Or"
date: 
output: 
  github_document:
    toc: true
---


Plots of soil water characteristics data set. Total curves = 15153

```{r cars}
library(ggplot2)

WRC<- read.csv("C:/Users/guptasu.D/Downloads/WRC_dataset_surya_et_al_2021_final.csv")

dim(WRC)

colnames(WRC)

unique(WRC$source_db)

```


## Bulk density (g/cm3) vs Data sources

```{r}
options(warn=-1)

ggplot(WRC, aes(x=source_db, y=db_od)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Organic carbon (%) vs Data sources

```{r}

ggplot(WRC, aes(x=source_db, y=oc)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Sand content (%) vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=sand_tot_psa_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Silt content (%) vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=silt_tot_psa_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Clay content (%) vs Data sources


```{r}

ggplot(WRC, aes(x=source_db, y=clay_tot_psa_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## pH vs Data sources

```{r}

ggplot(WRC, aes(x=source_db, y=ph_h2o)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Field measured saturated hydraulic conductivity (cm/day)  vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=ksat_field)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Lab measured saturated hydraulic conductivity (cm/day)  vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=ksat_lab)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Porosity (%) vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=porosity_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## VG shape parameter (1/m) vs Data sources

```{r}

ggplot(WRC, aes(x=source_db, y=alpha)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


## VG shape parameter vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=n)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Saturated water content (m3/m3) vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=thetas)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Residual water content (m3/m3) vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=thetar)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Root mean square error (m3/m3) vs Data sources


```{r}
ggplot(WRC, aes(x=source_db, y=RMSE)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))

```


