---
title: "Global soil hydraulic properties (GSHP) database"
author: "Surya Gupta, Andreas Papritz, Peter Lehmann, Tom Hengl, Sara Bonetti, Dani Or"
date: 
output: 
  github_document:
    toc: true
---


Plots of soil water characteristics data set. Total curves = 15153

```{r cars}
library(ggplot2)

WRC<- read.csv("C:/Users/guptasu.D/Downloads/WRC_dataset_surya_et_al_2021_final.csv")

dim(WRC)

colnames(WRC)

unique(WRC$source_db)

```


## Bulk density vs Data sources

```{r}
options(warn=-1)

ggplot(WRC, aes(x=source_db, y=db_od)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("db_od [", g/cm^{3},"]")), x = expression(paste("source_db [-]" )))

```

## Organic carbon vs Data sources

```{r}

ggplot(WRC, aes(x=source_db, y=oc)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("oc [%]")), x = expression(paste("source_db [-]" )))

```

## Sand content vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=sand_tot_psa_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("sand_tot_psa_percent [%]")), x = expression(paste("source_db [-]" )))


```

## Silt content vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=silt_tot_psa_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("silt_tot_psa_percent [%]")), x = expression(paste("source_db [-]" )))


```

## Clay content vs Data sources


```{r}

ggplot(WRC, aes(x=source_db, y=clay_tot_psa_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("clay_tot_psa_percent [%]")), x = expression(paste("source_db [-]" )))


```

## pH vs Data sources

```{r}

ggplot(WRC, aes(x=source_db, y=ph_h2o)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("ph_h2o [-]")), x = expression(paste("source_db [-]" )))


```

## Field measured saturated hydraulic conductivity  vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=ksat_field)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("ksat_field [cm/day]")), x = expression(paste("source_db [-]" )))


```

## Lab measured saturated hydraulic conductivity vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=ksat_lab)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("ksat_lab [cm/day]")), x = expression(paste("source_db [-]" )))


```

## Porosity vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=porosity_percent)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("porosity_percent [%]")), x = expression(paste("source_db [-]" )))


```

## vG shape parameter vs Data sources

```{r}

ggplot(WRC, aes(x=source_db, y=alpha)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("alpha [1/m]")), x = expression(paste("source_db [-]" )))


```


## vG shape parameter vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=n)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("n [-]")), x = expression(paste("source_db [-]" )))


```

## Saturated water content vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=thetas)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("thetas [", m^{3}/m^{3},"]")), x = expression(paste("source_db [-]" )))


```

## Residual water content vs Data sources

```{r}
ggplot(WRC, aes(x=source_db, y=thetar)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("thetar [", m^{3}/m^{3},"]")), x = expression(paste("source_db [-]" )))


```

## Root mean square error vs Data sources


```{r}
ggplot(WRC, aes(x=source_db, y=RMSE)) + geom_boxplot()+ theme(axis.text.x = element_text(angle = 90, hjust = 1))+labs( y= expression(paste("RMSE [", m^{3}/m^{3},"]")), x = expression(paste("source_db [-]" )))


```


